%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\parindent}{1.5em}
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.
\thispagestyle{plain} % No headers, just page numbers
%\setlength{\parskip}{1em}
First I would like to thank my Advisor Dr. Lijun Qian, of the Electrical and Computer Engineering department at Prairie View A\&M University. The endless support and opportunity he provided me is unexplainable. The door to Dr.Lijun Qian's  office was always open for me and whenever I faced problems and needed any advice he was always there to steer me to the right direction .

I would also like to thank Dr. Xishuang Dong, Post doc of Electrical engineering department, without his passionate participation and input, this thesis could not have been successfully conducted. 

This research work is supported in part by the U.S. Office of the Assistant Secretary of Defense for Research and Engineering (OASD(R\&E)) under agreement number FA8750-15-2-0119, and by the U.S. Army Research Office under agreement number W911NF-16-1-0496. The U.S. Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon. The views and conclusions contained herein are those of the authors and should not be interpreted as necessarily representing the official policies or endorsements, either expressed or implied, of the Office of the Assistant Secretary of Defense for Research and Engineering (OASD(R\&E)), the Army Research Office, or the U.S. Government.

I would also like to thank all the members of the CREDIT (Center of excellence in Research and Education for big military Data InTelligence) center for their support, they have not only helped me with their technical knowledge they are also the most friendly and helpful people I met. 

Finally I would like to thank my parents, my brothers, my sister-in-law, my uncle and aunt who are the only family I have in Texas for their unbelievable contribution and providing unfailing support and encouragement throughout my years of study and the process of researching and writing this thesis. This accomplishment would not have been possible without them. Thank you. 

\pagebreak{}

\ifx true false
\vspace*{\fill}
\begin{center}
A.M.D.G.
\end{center}
\vspace*{\fill}
\pagebreak{}
\fi
