
\chapter*{CURRICULUM VITA}
\addcontentsline{toc}{chapter}{VITA}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.

% Set your name here
\def\name{Safat Mahmood}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}
% Place name at left
\section*{\large \bf \name}
\begin{singlespace}

\begin{minipage}{0.45\linewidth}
  Prairie View A\&M University \\
  Department of Electrical and Computer Engineering \\
  P.O. Box 519, Prairie View, 77446
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (713) 377-8388 \\
    Email: & \url{safatmahmood@gmail.com} \\
  \end{tabular}
\end{minipage}


\section*{\large \bf Education}

\begin{itemize}
  \item M.S. Electrical and Computer Engineering, Prairie View A\&M University, 2015.

  \item B.Eng. Electrical/Electronics Engineering, Queen Mary University of London, 2012.

\end{itemize}

\section*{\large \bf Employment}

\begin{itemize}
\item Prairie View A\&M University, Research Assitant, 2015--2016.
\item Pacific Jeans Ltd., Assistant Engineer, 2013-14.
\end{itemize}

\section*{\large \bf Professional Skills}
\begin{itemize}
\item Solid foundation of theoretical knowledge, with sound practical electrical engineering/ programming skills, and strong/quick learning ability.
\item Natural Language Processing (NLP), Information Extraction \& sentiment analysis,Machine learning, Deep learning,Network and Cyber Security,Robotic Sensing, Semiconductors, Microcontrollers
\item Embedded system, assembly language , FPGA, C++, python, Matlab, HTML,CSS and many more.
\end{itemize}

\section*{\large \bf Achievements \& Social works}

%\subsection*{Journal Articles}

\begin{itemize}
%\item Joshua Bassey, Lijun Qian, Alexander Aved, Timothy Kroecker, 
%{\it Efficient Algorithm for Computation of Dempster-Shafer theoretic Conditionals for big Hard/Soft Data Fusion},
%      submitted.
%\item Large-scale image processing research cloud, 2014,
%      {\it CLOUD COMPUTING 2014: The Fifth International Conference on Cloud Computing, GRIDs, and Virtualization}.
\item Won First Prize in the 2016 IEEE Big data Competition in Chengdu, China.
\item Became Outstanding MSEE student of the department of Electrical and Computer Engineering, Prairie View A\&M University,2016-17
\item Got sponsored by British Airways for my Bachelors final year project.
\item Helped flood victims of Bangladesh from school.
\item Completed my jury services for Southwark crown court, London.

\end{itemize}

\end{singlespace}

% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%  \end{footnotesize}
%\end{center}



